---
title: "DS 301 H5"
author: "Mikaela Blount"
date: "4/2/2020"
output: html_document
---

Problem 1:
a)
π0 = 0.8
π1 = 0.2
P(X|Y=0) ~ N(2,3)
P(X|Y=1) ~ N(4,3)

b)
```{r}
mu0 = 2
mu1 = 4
sigma2 = 3


```


c)
```{r}
n=1000

1/(n-2)*(800*var(x0)+200*var(x1))
```


d)
```{r}
Y = rep(1,1000)

for(i in 1:1000){

if(X_train[i]<value-you-derived){

Y[i] = 0

}

}
```



e)


f)




g)





h)



Problem 2:
```{r}
library(dplyr)
spam <- read.csv("~/Downloads/spambase.data", header=FALSE)
spam = spam %>%
  rename(spamCol = V58)
```

a)
```{r}
spam$spamCol = as.numeric(spam$spamCol)

isSpam = spam %>%
  filter(spamCol == 1)

length(isSpam$spamCol)/length(spam$spamCol)*100

notSpam = spam %>%
  filter(spamCol == 0)

length(notSpam$spamCol)/length(spam$spamCol)*100
```
Spam: 39.40448%
Not spam: 60.59552%

b) I will spilt the dataset into spam and not spam, randomly arrange the rows, and then take 80% to train and 20% to test. I will full join the spam train and not spam and then do the same for spam test and not spam test thus preserving the correct ratios from above.
```{r}
set.seed(42)

rowsIsSpam <- sample(nrow(isSpam))
isSpamRandom <- isSpam[rowsIsSpam, ]
isSpamRandom = isSpamRandom %>%
  arrange()

len80percentIS = floor(nrow(isSpamRandom)*.8)
trainIsSpam = isSpamRandom[1:len80percentIS,]
testIsSpam = isSpamRandom[(len80percentIS+1):nrow(isSpamRandom),]

rowsNotSpam <- sample(nrow(notSpam))
notSpamRandom <- notSpam[rowsNotSpam, ]
notSpamRandom = notSpamRandom %>%
  arrange()

len80percentNS = floor(nrow(notSpamRandom)*.8)
trainNotSpam = notSpamRandom[1:len80percentNS,]
testNotSpam = isSpamRandom[(len80percentNS+1):nrow(notSpamRandom),]

train = full_join(trainIsSpam,trainNotSpam)
test = full_join(testIsSpam,testNotSpam)
```

c)
```{r}

```



Problem 3:
a) The misclassification rate is (25+32)/(25+32+40+121) = 0.2614679. It is worse to have a false negative because they person will not receive proper treatment and would spread the virus because they think they do not have the virus.

